\begin{longtable}{|>{\raggedright}m{2.5cm}|>{\raggedright}m{3.5cm}|>{\raggedright\arraybackslash}m{8cm}|}
    \caption{Components of the CAPSAM Pillars as shown in \ref{fig:CAPSAM_Pillars}.}
    \label{tab:CAPSAM_Pillars_Components} \\
    \hline
    \textbf{Pillar} & \textbf{Component} & \textbf{Explanation} \\
    \hline\hline
    \endhead

    \textbf{Culture} & Security-First Mindset & Fostering a security-first mindset across the organisation. \\
    \cline{2-3}
    & Top Management Involvement & Ensuring commitment from top management for necessary resources and support. \\
    \cline{2-3}
    & Agile \& DevSecOps & Embedding security into the agile development cycle and DevSecOps practices. \\
    \cline{2-3}
    & Customer Focused & Prioritising consumer data protection and building trust through embedded security. \\
    \hline\hline

    \textbf{Continuous} & Regular Risk Assessments & Conducting regular and dynamic risk assessments throughout the system's lifecycle. \\
    \cline{2-3}
    & Dynamic Threat Landscape & Continuously monitoring and adapting strategies to emerging risks. \\
    \cline{2-3}
    & Feedback Loop & Using insights from assessments and responses to refine security measures. \\
    \hline\hline

    \textbf{Auditing} & Regular Internal Audits & Regular audits to ensure compliance and assess security measure effectiveness. \\
    \cline{2-3}
    & Third-Party Reviews & Engaging external experts for unbiased security evaluations. \\
    \cline{2-3}
    & Penetration Testing & Simulating real-world attacks to identify and mitigate vulnerabilities. \\
    \hline\hline

    \textbf{Response} & Incident Response Plans & Developing and regularly updating plans for potential security incidents. \\
    \cline{2-3}
    & Immediate Action & Swift and decisive action to limit damage during security breaches. \\
    \cline{2-3}
    & Post-Incident Analysis & Analysing breaches to understand and address vulnerabilities. \\
    \cline{2-3}
    & Transparency & Clear communication with stakeholders about security incidents. \\
    \hline\hline

    \textbf{Proactive} & Worse-Case Planning & Proactive measures and worst-case scenario planning. \\
    \cline{2-3}
    & Security by Design & Integrating security into every phase of system development. \\
    \cline{2-3}
    & Employee Training & Regular training in cybersecurity best practices. \\
    \cline{2-3}
    & Threat Hunting & Actively searching for potential vulnerabilities and threats. \\
    \hline
\end{longtable}